Exploring Crete's Macroecology based on its soil Microbial Interactome

### 2024-01-04 manuscript.tex
add ancombc ref and fix italics

%\usepackage{showframe}

\graphicspath{{Fig/}}

@@

The island of Crete, Greece has been studied since the classical times for its' fauna \citep{Sidiropoulos_Polymeni_Legakis_2017,Anastasiou2018Tenebrionid}, flora \citep{Krimbas_2005} and ecosystems \citep{Grove1993}.
Crete is a continental island, fifth largest island of the mediterranean, a mediterranean biodiversity hotspot, model for desertification, climate change \citep{Kougioumoutzis2020} and habitat loss \citep{ISPIKOUDIS1993259},
elevation gradient \citep{trigas2013, FAZAN2017}, grasing impacts on ecosystems \citep{JouffroyBapicot2016} and evolutionary model \citep{POULAKAKIS2002}.
Yet the terrestrial microbial diversity has been unexplored.

@@

Python 3.11.4
Julia Version 1.9.3 \citep{Julia-2017}
R version 4.3.2 \citep{rcoreteam}
Network inferrence using FlashWeave 0.19.2 \citep{Tackmann2019}
Network analysis in igraph R package \citep{Csardi2006}
Differential abundance analysis with ANCOM-BC R package \citep{Lin2020}
Spatial analysis with the sf and stars R packages \citep{Pebesma2023}
U-CIE R package for coloring 3 dimentional data \citep{Koutrouli2022}
ggplot2 \citep{ggplot22016}
pheatmap \citep{Kolde2019}

>>>>

%\usepackage{showframe}
\usepackage[T1]{fontenc}
\graphicspath{{Fig/}}

@@

The island of Crete, Greece has been studied since the classical times for its' fauna \citep{Sidiropoulos_Polymeni_Legakis_2017,Anastasiou2018Tenebrionid}, flora \citep{Krimbas_2005} and ecosystems \citep{Grove1993}.
Crete is home to the only endemic mammal of Greece, the Cretan shrew (\textit{Crocidura zimmermanni}), more than 350 endemic arhropods, \# endemic plants among them a tree \textit{Zelkova abelicea}.
Crete is a continental island, fifth largest island of the mediterranean, a mediterranean biodiversity hotspot, model for desertification, climate change \citep{Kougioumoutzis2020} and habitat loss \citep{ISPIKOUDIS1993259},
elevation gradient \citep{trigas2013, FAZAN2017}, grasing impacts on ecosystems \citep{JouffroyBapicot2016} and evolutionary model \citep{POULAKAKIS2002}.
Yet the terrestrial microbial diversity has been unexplored.

@@

Python 3.11.4
Julia Version 1.9.3 \citep{Julia-2017}
R version 4.3.2 \citep{rcoreteam}
Network inferrence using FlashWeave 0.19.2 \citep{Tackmann2019}
Network analysis in igraph R package \citep{Csardi2006}
Differential abundance analysis with ANCOM-BC R package \citep{Lin2020,Lin2023}
Spatial analysis with the sf and stars R packages \citep{Pebesma2023}
U-CIE R package for coloring 3 dimentional data \citep{Koutrouli2022}
ggplot2 \citep{ggplot22016}
pheatmap \citep{Kolde2019}
